---
title: "DATA606HW6"
author: "jim lung"
date: "03-30-2017"
output: html_document
---

Graded: 6.6, 6.12, 6.20, 6.28, 6.44, 6.48

P. 313

6.6 2010 Healthcare Law. 
On June 28, 2012 the U.S. Supreme Court upheld the much debated
2010 healthcare law, declaring it constitutional. A Gallup poll released the day after this decision
indicates that 46% of 1,012 Americans agree with this decision. At a 95% confidence level, this
sample has a 3% margin of error. Based on this information, determine if the following statements
are true or false, and explain your reasoning.39
(a) We are 95% confident that between 43% and 49% of Americans in this sample support the
decision of the U.S. Supreme Court on the 2010 healthcare law.

False, it is a fact that 46% of Americans agree, it is not a sample population. 

(b) We are 95% confident that between 43% and 49% of Americans support the decision of the
U.S. Supreme Court on the 2010 healthcare law.

True, the margin of error is 3% at 95% confident, it mean 46%+3% and 46%-3%, (43% and 49%) as confidence interval.

(c) If we considered many random samples of 1,012 Americans, and we calculated the sample
proportions of those who support the decision of the U.S. Supreme Court, 95% of those sample
proportions will be between 43% and 49%.

False, the 95% confidence intervals is definited the population proportions.

(d) The margin of error at a 90% confidence level would be higher than 3%.

True, the population distribution will be narrow if it is lower confidence level

P.315

6.12 Legalization of marijuana, Part I. The 2010 General Social Survey asked 1,259 US residents:
¡§Do you think the use of marijuana should be made legal, or not?¡¨ 48% of the respondents
said it should be made legal.44
(a) Is 48% a sample statistic or a population parameter? Explain.

It is 48% a sample statisitic for 1259 US residents of all.

(b) Construct a 95% confidence interval for the proportion of US residents who think marijuana
should be made legal, and interpret it in the context of the data.

```{r}
# 95% confidence interval
zscore <-1.96

# sample size
n <-1259

# 48% of respondents thinks it should be legal
p <- 0.48

# Standard error
se <- sqrt(p*(1-p)/n)
se

# 95% confidence interval (upper, lower)
# margin of error (zscore*se)
upper <- p + zscore*se
lower <- p - zscore*se
ci <- c(upper, lower)
ci

```

(c) A critic points out that this 95% confidence interval is only accurate if the statistic follows a
normal distribution, or if the normal model is a good approximation. Is this true for these
data? Explain.

This is true, the normal model is a good approximation, if sampling distribution is nearly normal when the observations are independent, the p is 0.48 closely to half.

(d) A news piece on this survey¡¦s findings states, ¡§Majority of Americans think marijuana should
be legalized.¡¨ Based on your confidence interval, is this news piece¡¦s statement justified?

It is not justified because 95% confidence interval from 0.5 to 0.45.


P.316

6.20 Legalize Marijuana, Part II. As discussed in Exercise 6.12, the 2010 General Social
Survey reported a sample where about 48% of US residents thought marijuana should be made
legal. If we wanted to limit the margin of error of a 95% confidence interval to 2%, about how
many Americans would we need to survey ?

```{r }
# 95% confidence interval
zscore <-1.96

# margin of error
me <- 0.02

# zscore (95% confidence interval)
zscore <-qnorm(0.975)

# me = zscore*se
se <- me/zscore
se

# number of amercians,n
P <- 0.48
n <- (p * (1-p)) / se^2
n
# n=2397
```

P.319

6.28 Sleep deprivation, CA vs. OR, Part I. According to a report on sleep deprivation by the
Centers for Disease Control and Prevention, the proportion of California residents who reported
insufficient rest or sleep during each of the preceding 30 days is 8.0%, while this proportion is
8.8% for Oregon residents. These data are based on simple random samples of 11,545 California
and 4,691 Oregon residents. Calculate a 95% confidence interval for the difference between the
proportions of Californians and Oregonians who are sleep deprived and interpret it in context of
the data.53

```{r }
# 95% confidence interval
zscore <- 1.96
pc <- 0.08
nc <- 11545
po <- 0.088
no <-4691

# standard of error for california
sec <- sqrt(pc*(1-pc)/nc)
sec
# sec=0.0025

# standard of error for oregon
seo <- sqrt(po*(1-po)/no)
seo
# seo=0.0041

sepro <- sqrt(sec^2+seo^2)
sepro
# sepro=0.0048


lower<-(po-pc)-zscore*sepro
upper<-(po-pc)+zscore*sepro
ci <- c(upper, lower)
ci

# we canot reject null hypothesis, the difference is zero, because the zero contained in confidence interval.
```

P.323

6.44 Barking deer. Microhabitat factors associated with forage and bed sites of barking deer
in Hainan Island, China were examined from 2001 to 2002. In this region woods make up 4.8%
of the land, cultivated grass plot makes up 14.7% and deciduous forests makes up 39.6%. Of the
426 sites where the deer forage, 4 were categorized as woods, 16 as cultivated grassplot, and 61 as
deciduous forests. The table below summarizes these data.62

(a) Write the hypotheses for testing if barking deer prefer to forage
in certain habitats over others.

Null H0: it is no difference between each forage for deer
Alternative Ha: deer  prefer at least one of the forage

(b) What type of test can we use to answer this research question?

it is using the Chi-square test for one-way table

(c) Check if the assumptions and conditions required for this test
are satisfied.

The case likes independent for each case and it is at least 5 expected case for each particular scenario.

(d) Do these data provide convincing evidence that barking deer prefer
to forage in certain habitats over others? Conduct an appropriate
hypothesis test to answer this research question.

```{r}
# total, n=426
n<-426

obser<-c(4,16,67,345)

expected<-c(n*0.048,n*0.147,n*0.396,n*0.409)

chisq<-sum((obser-expected)^2/expected)
df<-4-1

pchisq(chisq,df,lower.tail=FALSE)

```

The p-value is 1.144396e-59 or 0, it is not reject the null that it is no difference between each forage for deer.


P.325

6.48 Coffee and Depression. Researchers conducted a study investigating the relationship
between caffeinated coffee consumption and risk of depression in women. They collected data
on 50,739 women free of depression symptoms at the start of the study in the year 1996, and
these women were followed through 2006. The researchers used questionnaires to collect data on
ca???einated co???ee consumption, asked each individual about physician-diagnosed depression, and
also asked about the use of antidepressants. The table below shows the distribution of incidences
of depression by amount of ca???einated coffee consumption.63

(a) What type of test is appropriate for evaluating if there is an association between co???ee intake
and depression?

Chi square test is used.

(b) Write the hypotheses for the test you identified in part (a).

H0 there is not difference in coffee among the depression yes no groups for women.

Ha: There is a difference in coffee among the depression groupings for women.

(c) Calculate the overall proportion of women who do and do not suffer from depression.

```{r}
depress <- 2607
nodepress <- 48132
total <- depress + nodepress
propdepress <- depress/total
propnodepress <- nodepress/total
propdepress
propnodepress
```

(d) Identify the expected count for the highlighted cell, and calculate the contribution of this cell
to the test statistic, i.e. (Observed ??? Expected)2/Expected.

```{r}
# Expected count for 2-6 per week, total=6617
expected <- propdepress*6617
expected
# expected count=339

observed <- 373
teststat <- ((observed-expected)^2)/expected
teststat
```
The contribution is 3.2.

(e) The test statistic is x2 = 20.93. What is the p-value?

```{r}
# p-value
test <- 20.93
df <- (5-1)*(2-1)
#df=4

pchisq(test,df,lower.tail = FALSE)



```

(f) What is the conclusion of the hypothesis test?

pvalue is less than 0.05, it is fail to reject the null hypothesis, it is not enough supporting the association between caffinated coffee consumption and depression.

(g) One of the authors of this study was quoted on the NYTimes as saying it was ¡§too early to
recommend that women load up on extra coffee¡¨ based on just this study.64 Do you agree with
this statement? Explain your reasoning.

I agree this statement, because depression may be caused by the other factors.