---
title: "DATA606HW3"
author: "jim lung"
date: "02-18-2017"
output: html_document
---
Question 3
Load Data



```{r setup, include=FALSE}
library(stringr)
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"   
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name

```



a. Use the tools of chapter to rearrang the vector so that all elements conform to the standard first_name last name.

To clear "Rev" and "Dr"


```{r }
Name_cleartitle<-unlist(str_replace(name,"[[:alpha:]]{2,}[.]",""))
Name_cleartitle

```
First Name:



```{r }
firstName <- unlist(str_extract(Name_cleartitle,"[[:alpha:]]{2,}[[:space:]]{1,}|[[:space:]]{1,}[[:alpha:]]{2,}"))
firstName

```
Last Name:



```{r }
lastName <- unlist(str_extract(Name_cleartitle,"[^[:punct:]][[:space:]][[:alpha:]]{2,}|[[:alpha:]]{2,}[[:punct:]]"))
lastName <- unlist(str_replace(lastName,"[[:alpha:]][[:space:]]", ""))
lastName <- unlist(str_replace(lastName,"[[:punct:]]", ""))
lastName

```

data.frame(firstName, lastName)

```{r }
data.frame(firstName, lastName)

```

b) Construct a logical vector indicating whether a character has a title(i.e., Rev. and Dr.)

TRUE of logical vector indicate has a title:
```{r }
title <- unlist(str_detect(name,"[[:alpha:]]{2,}[.]"))
title

```

Table of logical vector
```{r }
Table1<-data.frame(name,title)
Table1
```

c) Construct a logical vector indicating whether a character has a second name.

Logical vector indicate if has a second name.

```{r }
secondname <- unlist(str_detect(Name_cleartitle,"[[:alpha:]]{1,}[.]"))
secondname

```
Table of logical vector
```{r }
Table2<-data.frame(name,secondname)
Table2
```

4 Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

1.[0-9]+\\$
```{r }
example1 <-c ("123$","0","$123","0$","123$ab","123")
example1 <- str_detect(example1,"[0-9]+\\$")
example1
```

2. \\b[a-z]{1,4}\\b
```{r }
example2 <-c ("b4b","123tow","abfg123bb","skdfj&","dkk45b","123qef")
example2 <- str_detect(example2,"\\b[a-z]{1,4}\\b")
example2
```

3. .*?\\.txt$
```{r }
example3 <-c ("*?txt$","af.txt","abfg123bb","*adfd5b","dff")
example3 <- str_detect(example3,".*?\\.txt$")
example3
```

4. \\d{2}/\\d{2}/\\d{4}

```{r }
example4 <-c ("adf","af/123","12/12/1212","13/qw/1235","1/1/2032")
example4 <- str_detect(example4,".*\\d{2}/\\d{2}/\\d{4}")
example4
```

5. <(.+?)>.+?</\\1>

```{r }
example5 <-c ("<abc>abc</abc>","</\fgf>sdfd<s\12>","12/12/1212","<344>dfd<232>","<dfd>")
example5 <- str_detect(example5,"<(.+?)>.+?</\\1>")
example5
```

9. 
The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.

```{r }
message<-"clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
message<-unlist(str_extract_all(message, "[[:upper:].]{1,}"))
message <- cat(str_c(message,collapse = ""))

```
